Democratizing MPC

### 2017-10-03 OaklandSubmission/intro.tex
intro-flow-2

In this work, we develop and implement our framework \tool where the programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. The programmer is oblivious of the Our compiler automatically compiles it to a circuit framework consisting to both arithmetic and boolean gates as well share-conversion gates wherever required. We use ABY as the cryptographic backend. We give a type system, correctness ..... We evaluate our framework on ... and show performance comparable and even better than tailor made protocols.

\cite{lambdaps,wysteria}

>>>>

In this work, we develop and implement our framework \tool where the programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. The programmer is oblivious of the cryptographic backend being used. Our compiler automatically compiles it to a circuit framework consisting to both arithmetic and boolean gates as well share-conversion gates wherever required. We use ABY as the cryptographic backend. We give a type system, correctness ..... We evaluate our framework on ... and show performance comparable and even better than tailor made protocols. It is simple to program in our framework and our work provides a meaningful baseline for future works designing tailor made protocols for specific functionalities.

\subsection{\tool: Overview and Contributions}

\noindent\textbf{Scaling to large programs.} Describe pipeling here...

\noindent\textbf{Related Work}
\cite{lambdaps,wysteria}
